Blame and Coercion: Together Again for the Second Time

### 2019-10-17 paper.tex
added proposition lazy UD monoid
explain why cod

Secondly, the definition of normal coercion lies unnecessarily on top 
of coercion: all coercions are normal when they are initially constructed, and 
\citet{siek2012interpretations} have shown an function that 
composes and produces normal coercions.
%
\todo[inline]{Many researchers would view this as a positive thing,
  not a negative. For example, the notion of normal forms comes up
  over and over again in mathematics and logic. -Jeremy
\\ --- \\
I guess having a notion of normal forms is more convenient when a 
notion of normalization is convenient. But we don't even need a notion of 
normalization for cast representations. -KC}

@@

\figref{fig:blame-static} defines the syntax of cast calculi and its
static semantics. We extend the syntax in \citet{siek2009exploring} with sum 
types and product types. Besides, we annotate function codomain explicitly 
because we need the codomain when evaluating cast calculus with hypercoercions.
\todo[inline]{Which previous definitions are you refering to?  What
  are the little changes? -Jeremy
\\ --- \\ Fixed -KC}
\todo[inline]{The term typing rule for casts is broken. -Jeremy
\\ --- \\ Fixed -KC}
\todo[inline]{Why do you annotate the codomain of lambda abstractions
	explicitly? -Jeremy
	\\---\\
	Because I apply $ id(\cdot) $ to the codomain in the HC CEK. -KC
        \\---\\
        The answer you put in the text is to vague. -JS
        }
Let $ T $ range over types. A type is either the dynamic type $ \star $
(a.k.a. $ \mathtt{Dyn} $, $ \mathbb{?} $, or $ \mathtt{Unknown} $), 
or a pre-type. 
Let $ P $ range over pre-types. Every pre-type is a type with a type 
constructor at the top. For simplicity, we only have one base type, $ \POOunit 
$. 
Other pre-types are functions, products, and sums.

>>>>

Secondly, the definition of normal coercion lies unnecessarily on top 
of coercion: all coercions are normal when they are initially constructed, and 
\citet{siek2012interpretations} have shown an function that 
composes and produces normal coercions.
%
\todo[inline]{Many researchers would view this as a positive thing,
  not a negative. For example, the notion of normal forms comes up
  over and over again in mathematics and logic. -Jeremy
\\ --- \\
I guess having a notion of normal forms is more convenient when a 
notion of normalization is convenient. But we don't even need a notion of 
normalization for cast representations. -KC
\\ --- \\
FWIW, I agree with you. But the point is that the argument is not
likely to be convinving to the reader, so we're probably better off
not wasting space on it. -JS
}

@@

\figref{fig:blame-static} defines the syntax of cast calculi and its
static semantics. We extend the syntax in \citet{siek2009exploring} with sum 
types and product types. Besides, we annotate function codomain explicitly 
because we need to compute identity hypercoercion for the codomain when 
evaluating cast calculus with hypercoercions.
\todo[inline]{Which previous definitions are you refering to?  What
  are the little changes? -Jeremy
\\ --- \\ Fixed -KC}
\todo[inline]{The term typing rule for casts is broken. -Jeremy
\\ --- \\ Fixed -KC}
\todo[inline]{Why do you annotate the codomain of lambda abstractions
	explicitly? -Jeremy
	\\---\\
	Because I apply $ id(\cdot) $ to the codomain in the HC CEK. -KC
        \\---\\
        The answer you put in the text is too vague. -JS
        \\---\\
        Fixed. -KC}
Let $ T $ range over types. A type is either the dynamic type $ \star $
(a.k.a. $ \mathtt{Dyn} $, $ \mathbb{?} $, or $ \mathtt{Unknown} $), 
or a pre-type. 
Let $ P $ range over pre-types. Every pre-type is a type with a type 
constructor at the top. For simplicity, we only have one base type, $ \POOunit 
$. 
Other pre-types are functions, products, and sums.
